POMDP comparisons across sigma_m, sigma_g

### 2018-01-06 appendix/appendixB.Rmd
updated appendix B alphas

```{r}
options(mc.cores = parallel::detectCores()) # Reserve ~ 10 GB per core
log_dir <- "pomdp_historical"
```

@@

```{r eval=FALSE}
dir.create(log_dir)

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 2e-6,
             timeout = 20000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

>>>>

```{r}
options(mc.cores = parallel::detectCores()) # Reserve ~ 10 GB per core
log_dir <- "appendixB_alphas"
```

@@

```{r eval=TRUE}
dir.create(log_dir)
options(mc.cores = 1)

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 2e-6,
             timeout = 25000,
             log_dir = log_dir,
             log_data = log_data)
    })
)
